Promotors' reports on the first draft of the thesis document.

### 2020-03-20 Gus-thesis.tex
First draft completed!
Second review version
Third review

%%
%% This code was generated from the thesis template of Adam Cooman--Evi Van Nechel.
%% It has been adapted slightly by Gustavo Quintana.
%% Compile with: pdflatex --shell-escape -synctex=1 -interaction=nonstopmode Gus-thesis.tex 
%%
\documentclass[english, british, BCOR=5mm, DIV=12, fontsize=10pt]{scrbook}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage[paperwidth=17cm, paperheight=24cm]{geometry} % \usepackage[hmargin=1.5cm, textheight=25cm]{geometry}
\geometry{verbose, tmargin=2.5cm, bmargin=3cm, lmargin=2.5cm, rmargin=2cm}
\setcounter{secnumdepth}{2}
\setcounter{tocdepth}{2}
\setlength{\parskip}{\medskipamount}
\setlength{\parindent}{0pt}
\synctex=-1
\usepackage{color}
\definecolor{note_fontcolor}{rgb}{0.800781, 0.800781, 0.800781}
\usepackage{amsfonts, amsmath, amssymb, amsthm, amsbsy, array, babel, booktabs, bm, float, graphicx, lineno, mathdots, mathptmx, mathtools, newproof, pgf, subcaption, textcomp, times, units, verbatim, xcolor}
\usepackage[unicode=true, pdfusetitle, bookmarks=true, bookmarksnumbered=false, bookmarksopen=false, breaklinks=true, pdfborder={0 0 0}, pdfborderstyle={}, backref=false, colorlinks=false]{hyperref}
\usepackage[outdir=./]{epstopdf}
\usepackage{tikz, circuitikz}
\usetikzlibrary{shapes, arrows, calc, patterns, decorations.pathmorphing, decorations.markings, positioning}

@@

	\begin{tabular}{@{}lll@{}}
	\textbf{\small PROMOTERS}		& &	{\small prof. dr. ir. Ivan Markovsky}				\\
				& &		{\footnotesize{}Vrije Universiteit Brussel, Belgium}\\[0.3em]
				& &	\small prof. dr. ir. Rik Pintelon				\\
				& &		{\footnotesize{}ELEC Department, Vrije Universiteit Brussel, Belgium.}	\\[0.3em]
				\\
	\textbf{\small MEMBERS OF THE JURY}	&	&\small prof. dr. ir. Patrick Guillaume (President)		\\
				&	&{\footnotesize{}MECH Department, Vrije Universiteit Brussel, Belgium.}	\\[0.3em]
				% &								\\
				&	&\small prof. dr. ir. Roger Vounckx (Vice-President)				\\
				&	&{\footnotesize{}ETRO Department, Vrije Universiteit Brussel, Belgium.}	\\[0.3em]
				% &								\\
				&	&\small dr. ir. Philippe Dreesen (Secretary)					\\
				&	&{\footnotesize{}ELEC Department, Vrije Universiteit Brussel, Belgium.}				\\[0.3em]
				% &								\\
				&	&\small dr. ir. Nikolaos Deligiannis \\
				&	&{\footnotesize{}ETRO Department, Vrije Universiteit Brussel, Belgium.} 			\\[0.3em]
				% &								\\
				&	&\small prof. dr. ir. Lyudmila Mihaylova 		\\
				&	&{\footnotesize{}ACSE Department, University of Sheffield, United Kingdom.} \\
								% &								\\
				&	&\small prof. dr. ir. Stephane Chretien  		\\
				&	&{\footnotesize{}ERIC Laboratory, University Lyon 2, France.} \\
								% &								\\
				&	&\small prof. dr. ir. Guillaume  Merc\`ere 		\\
				&	&{\footnotesize{}LIAS Laboratory, Universit\'e de Poitiers, France.} \\
\end{tabular}

@@

{\footnotesize{}Cover design by ...}\\
{\footnotesize{}Background image by ...}{\footnotesize\par}
{\footnotesize{}~}{\footnotesize\par}

{\footnotesize{}$\copyright$ February 2019 Gustavo Quintana Carapia.}\\
{\footnotesize{}~}{\footnotesize\par}

@@

\include{Extras/Acknowledgements}

@@

@@

\include{Summary/Summary}

@@

>>>>

%%
%% This code was generated from the thesis template of Adam Cooman--Evi Van Nechel.
%% It has been adapted slightly by Gustavo Quintana.
%% Compile with: 
%% cd C:\GusDocs\org\thesis\Gus-thesis
%% pdflatex --shell-escape -synctex=1 -interaction=nonstopmode Gus-thesis.tex 
%%
\documentclass[english, british, BCOR=5mm, DIV=12, fontsize=10pt]{scrbook}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage[paperwidth=17cm, paperheight=24cm]{geometry} % \usepackage[hmargin=1.5cm, textheight=25cm]{geometry}
\geometry{verbose, tmargin=2.5cm, bmargin=3cm, lmargin=2.5cm, rmargin=2cm}
\setcounter{secnumdepth}{2}
\setcounter{tocdepth}{2}
\setlength{\parskip}{\medskipamount}
\setlength{\parindent}{0pt}
\synctex=-1
\usepackage{color}
\definecolor{note_fontcolor}{rgb}{0.800781, 0.800781, 0.800781}
\usepackage{amsfonts, amsmath, amssymb, amsthm, amsbsy, array, babel, booktabs, bm, float, graphicx, lineno, mathdots, mathptmx, mathtools, newproof, pgf, subcaption, textcomp, times, units, verbatim, xcolor}
\usepackage[unicode=true, pdfusetitle, bookmarks=true, bookmarksnumbered=false, bookmarksopen=false, breaklinks=true, pdfborder={0 0 0}, pdfborderstyle={}, backref=false, colorlinks=false]{hyperref}
\usepackage[outdir=./]{epstopdf}
\usepackage{tikz, circuitikz}
\usetikzlibrary{shapes, arrows, calc, patterns, decorations.pathmorphing, decorations.markings, positioning}

@@

	\begin{tabular}{@{}lll@{}}
	\textbf{\small PROMOTERS}		& &	{\small prof. dr. ir. Ivan Markovsky}				\\
				& &		{\footnotesize{}ELEC Department, Vrije Universiteit Brussel, Belgium}\\[0.3em]
				& &	\small prof. dr. ir. Rik Pintelon				\\
				& &		{\footnotesize{}ELEC Department, Vrije Universiteit Brussel, Belgium}	\\[0.3em]
				\\
	\textbf{\small MEMBERS OF THE JURY}	&	&\small prof. dr. ir. Patrick Guillaume (President)		\\
				&	&{\footnotesize{}MECH Department, Vrije Universiteit Brussel, Belgium}	\\[0.3em]
				% &								\\
				&	&\small prof. dr. ir. Roger Vounckx (Vice-President)				\\
				&	&{\footnotesize{}ETRO Department, Vrije Universiteit Brussel, Belgium}	\\[0.3em]
				% &								\\
				&	&\small dr. ir. Philippe Dreesen (Secretary)					\\
				&	&{\footnotesize{}ELEC Department, Vrije Universiteit Brussel, Belgium}				\\[0.3em]
				% &								\\
				&	&\small dr. ir. Nikolaos Deligiannis \\
				&	&{\footnotesize{}ETRO Department, Vrije Universiteit Brussel, Belgium} 			\\[0.3em]
				% &								\\
				&	&\small prof. dr. ir. Lyudmila Mihaylova 		\\
				&	&{\footnotesize{}ACSE Department, University of Sheffield, United Kingdom} \\
								% &								\\
				&	&\small prof. dr. ir. Stephane Chretien  		\\
				&	&{\footnotesize{}ERIC Laboratory, University Lyon 2, France} \\
								% &								\\
				&	&\small prof. dr. ir. Guillaume  Merc\`ere 		\\
				&	&{\footnotesize{}LIAS Laboratory, Universit\'e de Poitiers, France} \\
\end{tabular}

@@

%{\footnotesize{}Cover design by ...}\\
%{\footnotesize{}Background image by ...}{\footnotesize\par}
%{\footnotesize{}~}{\footnotesize\par}

{\footnotesize{}$\copyright$ February 2020, Gustavo Quintana Carapia.}\\
{\footnotesize{}~}{\footnotesize\par}

@@

%\include{Extras/Acknowledgements}

@@

\include{Extras/Summary}

@@

@@

\vspace{-0.5cm}
